ASHA 2023 Listening Effort Data Analysis

### 2023-10-27 ASHA 2023 Analysis/data_analysis.Rmd
Streamlining code

data <- rio::import("Cleaned Data/cleaned_data.csv") %>%
  # removing trials with missing rep accuracy: 3 trials removed
  dplyr::mutate(rep_acc = ifelse(rep_acc == "", NA, rep_acc)) %>%
  dplyr::filter(!is.na(rep_acc))

@@

perceived_effort_df <- data %>%
  dplyr::select(subject, trial, speaker, effort_rating, rep_acc, code) %>%
  dplyr::distinct() %>%
  # Creating a trial variable that codes trial 6 (i.e. the first experimental trial) as 0.
  dplyr::mutate(trial_c = trial - 6) %>%
  # Releveling speaker variable
  dplyr::mutate(speaker = as.factor(speaker),
                speaker = fct_relevel(speaker, "Control", "ALS")) %>%
  # For this particular analysis, we are just looking at results for accurate repetition
  # However, the final project will look at rep_acc too
  dplyr::filter(rep_acc == "accurate")

>>>>

data <- rio::import("Cleaned Data/cleaned_data.csv") %>%
  # removing trials with missing rep accuracy: 3 trials removed
  dplyr::mutate(rep_acc = ifelse(rep_acc == "", NA, rep_acc)) %>%
  dplyr::filter(!is.na(rep_acc)) %>%
  # Releveling speaker variable
  dplyr::mutate(speaker = as.factor(speaker),
                speaker = fct_relevel(speaker, "Control", "ALS")) %>%
  # Creating a trial variable that codes trial 6 (i.e. the first experimental trial) as 0.
  dplyr::mutate(trial_c = trial - 6)

@@

perceived_effort_df <- data %>%
  dplyr::select(subject, trial, speaker, effort_rating, rep_acc, code) %>%
  dplyr::distinct() %>%
  # For this particular analysis, we are just looking at results for accurate repetition
  # However, the final project will look at rep_acc too
  dplyr::filter(rep_acc == "accurate")
